---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# targit

[![CRAN](https://www.r-pkg.org/badges/version/targit)](https://CRAN.R-project.org/package=targit)
[![status](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![check](https://github.com/wlandau/targit/workflows/check/badge.svg)](https://github.com/wlandau/targit/actions?query=workflow%3Acheck)
[![codecov](https://codecov.io/gh/wlandau/targit/branch/main/graph/badge.svg?token=3T5DlLwUVl)](https://codecov.io/gh/wlandau/targit)
[![lint](https://github.com/wlandau/targit/workflows/lint/badge.svg)](https://github.com/wlandau/targit/actions?query=workflow%3Alint)

Version control systems such as Git help researchers track changes and history in data science projects, and the [`targets`](https://docs.ropensci.org/targets/) package minimizes the computational cost of keeping the latest results reproducible and up to date. The `targit` package combines these two capabilities. The [`targets`](https://docs.ropensci.org/targets/) data store becomes a version control repository and stays synchronized with the Git repository of the source code. Users can switch commits and branches without invalidating the [`targets`](https://docs.ropensci.org/targets/) pipeline.

## Installation

Type | Source | Command
---|---|---
Release | CRAN | `install.packages("targit")`
Development | GitHub | `remotes::install_github("wlandau/targit")`
```

## Citation

```{r, warning = FALSE}
citation("targit")
```
